Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2019-01-30 paper/snakemajoranas.tex
small changes to the paper

\comment{The introduction of an SN interface at many angles also increases performance.}
Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part will eventually scatter with a perpendicular surface.
This means that for transversal modes the transparency of the NS interface will increase.

@@

\comment{We calculate the topological phase diagram using the gap size.}
We calculate the gap by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here

\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase and Zeeman field.
We also see some additional gap closings which are due to the BDI symmetry class, creating quite an unstable region.
As expected, for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.

>>>>

\comment{The introduction of an SN interface at many angles also increases performance.}
Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part will eventually scatter with a near perpendicular surface.
This means that for transversal modes the transparency of the NS interface will increase.

@@

\comment{We calculate the topological phase diagram using the gap size.}
We calculate the gap $E_\textrm{gap}$ by finding the absolute minimum of the spectrum $E_\textrm{gap}=\min{|E(k)|}$.
Noting the gap closings and the fact we know the topology for the non-zigzag system, we can infer the topology of the system with zigzag modulation. % Bas: I don't understand what is written here

\comment{The phase diagram does not change much, except we see a cleaner spectrum as a result of the D class symmetry. }
Similar to what is described by Pientka et. al~\cite{pientka2017topological}, we see that the ribbon topology has a diamond like structure as a function of phase $\phi$ and Zeeman field $E_Z$.
We also observe additional gap closings which are due to the BDI symmetry that is present.
As expected for the zigzag system, the magnitude of the gap is significantly improved, whilst maintaining the diamond like shape.
As the zigzag shape destroys the additional symmetry, moving it to class D, we see a more clean topological region.
